---
title: "Report_Project1"
author: "R. Ruiz-Cruz"
date: "12/08/2016"
output: html_document
---
## 1.- Load the data
The data for the analysis is included in the archive "activity.csv". This archive is loaded and stored in the variable _data_.

```{r}
data <- read.csv("activity.csv",sep=",")
head(data)
```

The data have three columns named _steps_, _date_, _interval_.

## 2.- Histogram of the total number of steps taken each day
The total number of steps taken each day is calculated and it is show in a histogram.

```{r}
totalsteps <- with(data,tapply(steps,date,sum))
hist(totalsteps,breaks = 15)
```

The basic statistical information can be obtained by the command 'summary'.
```{r}
summary(data)
```

## 3.- Mean and median number of steps taken each day
The information presented above is calculated considering the all the data. The mean and median of the steps taken each day can be give us an extra information.
```{r}
mean_day <- with(data,tapply(steps,date,mean))
median_day <- with(data,tapply(steps,date,median))
mean_day
median_day
```

## 4.- Time series plot of the average number of steps taken
The average number of steps can be more friendly if the information is presented in a plot.
```{r}
fdates <- as.Date(unique(data$date))
plot(data$steps,type="l",main="Average number of steps",xlab = "5-min intervals",ylab = "steps")
```

## 5.-The 5-minute interval that, on average, contains the maximum number of steps
The 5-minute interval with tje maximum number of steps is obtained as follows:
```{r}
ind <- which.max(data$steps);
data[ind,]
```

## 6.- Strategy for imputing missing data
In order discrad the missing data, we can obtain a subet of _data_ considering only the information where the steps number is no "NA" (_!is.na(data$steps)_). The new data is stored in the variable _data0_.
```{r}
data0 <- subset(data,!is.na(data$steps))
data0$date <- as.Date(data0$date)
head(data0)
```

## 7.- Histogram of the total number of steps taken each day after missing values are imputed
Now, we can obtain again the total number of steps each day using the new variable _data0_.
```{r}
totalsteps1 <- with(data0,tapply(steps,date,sum))
totalsteps1
hist(totalsteps1,breaks=15)
```

## 8.- Comparison the average number of steps taken per 5-minute interval across weekdays and weekends
The steps average in the wekkends and the weekdays can be obtained as follows:

```{r}
m1 <- mean(data0$steps[!grepl("sá¡b|dom",weekdays(data0$date,abbreviate = TRUE))])
m2 <- mean(data0$steps[grepl("sá¡b|dom",weekdays(data0$date,abbreviate = TRUE))])
m1
m2
barplot(height = cbind(weekdays = m1,weekends = m2),main = "Steps Average",ylab = "steps")
```